\chapter*{Preface}
First, I would like to thank my supervisors Jim Tørresen and Ryo Kurazume, for their support, guidance, and patience during the development of this project. Second, my HR manager Marit Flendstad Kruse, for her assistance in letting me combine work with the writing of this thesis. Last, I would like to thank everyone at the Kurazume-lab for their welcome and help during my stay at Kyushu University, and my friends and family for proofreading and encouragement.

The subtitle, Both Eyes Open, has a double meaning: In this paper, we will explore the world in 3D. The biological way to achieve depth vision is by using two eyes, hence both eyes open. The other way to interpret the subtitle is tied with the small figure on the front page. In Japanese, the saying translated as "Both Eyes Open" refers to the Daruma figure. 

When one is working toward a goal, such as completing a thesis, one can purchase a Daruma figure from a temple. When bought, the Daruma has blank eyes - they are closed. The buyer then paints in one eye, asking for the Darumas help in completing their goal. In exchange for the Darumas help, the buyer promises to paint in the other eye. One significant detail about the Daruma is that it is weighted on the bottom.  If it should ever falter and fall over, it will right itself back up and continue on its way to completing the goal.

The ability to right yourself up for every setback has been of particular inspiration to me during my work on this thesis. This is why I have placed the figure on the front page; as a personal helper.


